
\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{parskip}
\usepackage{hyperref}

\begin{document}

\noindent
\textbf{Eliã Rafael de Lima Batista} \\
\href{mailto:o.elia.batista@gmail.com}{o.elia.batista@gmail.com} \\
+41 77 992 5544 \\
\href{https://linkedin.com/in/e-batista}{linkedin.com/in/e-batista} \\
\href{https://elbatista.github.io}{elbatista.github.io}

\vspace{1em}

May 19, 2025 \\
\vspace{1em}

Dear Relai Team,

\vspace{1em}

As a seasoned software engineer with over a decade of experience -- including several years building mobile apps with React Native -- I’m excited to apply for the \textbf{Senior React Native Developer} position at Relai. Your mission to make Bitcoin simple and accessible deeply resonates with me, and I’d be honored to contribute to your fast-growing team.

During my time at \textit{Compasso UOL}, I led the development of cross-platform mobile applications using \textbf{React Native}, \textbf{TypeScript}, and \textbf{RESTful APIs}, delivering seamless user experiences for large-scale clients. I’m proficient with \textbf{Redux} for state management and I like to follow the \textbf{MVVM (Model-View-ViewModel) pattern} to ensure clean separation of concerns and maintainable codebases. My engineering mindset values clean code, performance, and maintainability, and I bring this into every project I touch.


Currently, I’m pursuing a \textbf{PhD in Informatics at the University of Lugano (USI)}, where my research focuses on dependable distributed systems. This academic rigor complements my industry experience, especially when working on robust, scalable architectures. I also developed \href{https://wondersofswitzerland.com}{wondersofswitzerland.com}, a personal hobby project built with Next.js, showing my passion for creating polished digital experiences from scratch.

Beyond my technical skills, I thrive in remote-first teams, communicate clearly, and love mentoring fellow developers -- values I see reflected in Relai’s culture. The idea of building tools that help individuals and businesses save in Bitcoin is not only technically exciting but personally meaningful.

\vspace{1em}

Thank you for considering my application. I would love to discuss how I can help shape the next generation of Relai’s mobile app. I’m looking forward to hearing from you.

\vspace{1em}

Warm regards, \\
\textbf{Eliã Rafael de Lima Batista}

\end{document}
