\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{parskip}
\usepackage{hyperref}

\begin{document}

\noindent
\textbf{Eliã Rafael de Lima Batista} \\
\href{mailto:o.elia.batista@gmail.com}{o.elia.batista@gmail.com} \\
+41 77 992 5544 \\
Via Nava 22a, Pregassona, Lugano, Switzerland \\
\href{https://linkedin.com/in/e-batista}{linkedin.com/in/e-batista} \\
\href{https://elbatista.github.io}{elbatista.github.io}

\vspace{1em}

Jun 11, 2025 \\
\vspace{1em}

Dear Lastminute.com Team,

\vspace{1em}


I am writing to express my interest in the Senior Software Engineer position in your Flight Ancillaries team in Chiasso. As a PhD researcher in Distributed Systems at Università della Svizzera italiana (USI) with over a decade of experience in software engineering, I bring a strong foundation in backend development, distributed architectures, and system scalability — all aligned with your mission of powering millions of travelers' journeys.

Throughout my career, I have designed and implemented robust and high-performing systems using the Java ecosystem, with experience extending to Kotlin and functional programming concepts. My work has always been shaped by clean code practices, SOLID principles, and Agile methodologies — values I see emphasized in your engineering culture.

Currently, I work on dependable distributed systems with a focus on State Machine Replication, high-throughput scheduling, and fault-tolerant communication overlays. This includes designing resilient infrastructure, optimizing performance, and driving technical solutions that serve real-world demands — experience I am eager to apply in building scalable and secure microservices in your fast-paced environment.

What excites me most about this opportunity is the chance to combine two passions: cutting-edge software engineering and travel. I admire your commitment to enhancing the travel experience for millions, and I would be proud to contribute to this vision through high-quality, impactful code.

I would welcome the opportunity to bring my expertise and enthusiasm to your team in Chiasso. Thank you for considering my application. I am looking forward to the possibility of discussing how I can contribute to your mission.


\vspace{1em}

Best regards, \\
\textbf{Eliã Rafael de Lima Batista}

\end{document}
