\documentclass[a4paper,10pt]{letter}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{left=2.5cm,right=2.5cm,top=2cm,bottom=2cm}

\begin{document}

\begin{letter}{To the Hiring Team\\Bending Spoons\\Milan, Italy}
\opening{Dear Bending Spoons Team,}

I am writing to express my strong interest in the Software Engineer position at Bending Spoons. As a PhD researcher in dependable distributed systems, with a background in both academia and industry, I am enthusiastic about joining a company that combines technical excellence, operational effectiveness, and a bold vision for value creation.

Currently, I am living in Lugano, Switzerland, and conducting my PhD in a cotutelle program between Università della Svizzera italiana (USI) and PUC-RS in Brazil, under the supervision of Prof. Fernando Pedone. My research focuses on improving state machine replication systems through efficient parallel scheduling, optimized state management, and fault-tolerant communication overlays. My work requires a balance of rigorous reasoning, innovation, and a constant drive for simplification—all of which align closely with Bending Spoons’ engineering principles.

Before entering academia, I worked as a senior software engineer in Brazil, where I delivered production-grade systems using a range of technologies and architectural styles. Whether dealing with monolithic applications or microservices, I’ve always sought the best tool for the task—be it Python, Java, gRPC, or containerized environments like Docker and Kubernetes.

What excites me most about Bending Spoons is your dual focus on high-impact execution and personal growth. I am particularly inspired by your strategy of combining the discipline of capital allocation with hands-on software development. I am eager to contribute to this model, building software that scales effectively while growing alongside talented, driven teammates.

Thank you for considering my application. I would be thrilled to further discuss how my experience and values align with your team’s goals.

\closing{Sincerely,\\Eliã Batista}
\end{letter}

\end{document}
