

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{changepage}
\usepackage{ragged2e} % add this in the preamble


%----------FONT OPTIONS----------
% sans-serif
\usepackage[sfdefault]{FiraSans}
\usepackage[sfdefault]{roboto}
\usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% \pagestyle{fancy}
% \fancyhf{} % clear all header and footer fields
% \fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{.3in}
\addtolength{\topmargin}{-.5in}
% \addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small \justifying{
    {#1 }%\vspace{2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\huge \scshape Eliã Rafael de Lima Batista} \\ \vspace{15pt}
    \small 77-992-5544 $|$ \href{mailto:o.elia.batista@gmail.com}{\underline{o.elia.batista@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/e-batista}{\underline{linkedin.com/in/e-batista}} $|$
    \href{https://elbatista.github.io}{\underline{elbatista.github.io}} \\
    \vspace{5pt}
    \small 6963 Pregassona, TI, Switzerland
\end{center}

\vspace{2pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textsc{Ph.D.} in Informatics}{2021 -- Present}
      {Università della Svizzera Italiana (USI)}{Lugano, Switzerland}
      \resumeSubheading
      {\textsc{M.Sc.} in Computer Science}{2018 -- 2020}
      {Pontifical Catholic University of Rio Grande do Sul (PUC-RS)}{Porto Alegre, Brazil}
\resumeSubheading
      {\textsc{B.Sc.} in Computer Science}{2006 -- 2011}
      {Pontifical Catholic University of Rio Grande do Sul (PUC-RS)}{Porto Alegre, Brazil}

  \resumeSubHeadingListEnd


  \vspace{2pt}

  \section{Professional Summary}

  \begin{adjustwidth}{0.15in}{0pt}
  \small
  \justifying

  Senior Software Engineer with extensive experience in backend system design, high-availability architecture, and distributed systems. Proficient in \textbf{Java}, \textbf{Go}, \textbf{Node.js}, and \textbf{ReactJS}, with strong expertise in RESTful API design, relational (MySQL, SQLServer) and distributed NoSQL databases (Mongo, Firebase). Experienced in capacity planning, performance optimization, debugging, and cloud deployment, with a focus on scalability, reliability, and security. Demonstrated technical leadership, mentoring, and cross-team collaboration skills.

  \end{adjustwidth}

  \vspace{2pt}
%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Research and Development}{2021 -- Present}
      {Università della Svizzera Italiana (USI)}{Lugano, Switzerland}
      \resumeItemListStart
      \resumeItem{Designed and implemented backend services and distributed system components using \textbf{Go}, \textbf{Java}, and \textbf{Python} with a focus on high availability, fault tolerance, and performance optimization.}
      \resumeItem{Managed Linux clusters and distributed environments for testing and research, simulating large-scale deployments and recovery scenarios.}
      \resumeItem{Provided mentorship and guidance to junior engineers and students on system architecture, debugging, and code optimization.}
      \resumeItem{Authored and reviewed technical documentation for distributed components and API design.}
      
      \resumeItemListEnd
      
    \resumeSubheading
      {Senior Software Developer}{2017 -- 2020}
      {Compasso UOL}{Brazil, RS}
      \resumeItemListStart
      \resumeItem{Developed scalable backend and frontend services and RESTful APIs using \textbf{Node.js} and \textbf{ReactJS}, integrating with relational and NoSQL databases for enterprise applications.}
      \resumeItem{Led backend development projects, ensuring adherence to high-availability standards, fault-tolerant design, and efficient data handling.}
      \resumeItem{Collaborated with cross-functional teams to define technical strategy, project priorities, and deliverables.}
      \resumeItem{Participated in projects with CI/CD pipelines and containerized deployments using Docker.}
      
      \resumeItemListEnd

    %  \clearpage

    \resumeSubheading
      {System Analyst}{2014 -- 2017}
      {Bem Promotora}{Brazil, RS}
      \resumeItemListStart
      \resumeItem{Developed and maintained \textbf{ERP modules} for a credit payroll loan financial company linked to Banrisul, a major bank in Southern Brazil.}
      \resumeItem{Analyzed, documented, and communicated new system features to the development team to improve business process efficiency.}
      \resumeItem{Implemented complex business rules and data processing using \textbf{SQL Server} stored procedures for accurate loan management and reporting.}
        \resumeItemListEnd
     

    \resumeSubheading
      {Software Developer}{2010 -- 2013}
      {DBServer}{Brazil, RS}
      \resumeItemListStart
      \resumeItem{Developed and customized ERP modules tailored for a major fuel retail network (Ipiranga) in Brazil, improving operational efficiency and sales tracking.}
      \resumeItem{Integrated and managed backend logic with \textbf{SQL Server} for efficient data storage and retrieval.}
     \resumeItemListEnd

     \resumeSubheading
     {Software Developer}{2008 -- 2010}
     {Vensis}{Brazil, RS}
     \resumeItemListStart
     \resumeItem{Built and maintained general-purpose ERP modules, adaptable for various enterprise environments.}
     \resumeItem{Optimized \textbf{SQL Server} queries and stored procedures to boost system performance and data consistency.}
     \resumeItemListEnd


  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
% \section{Projects}
%     \resumeSubHeadingListStart
%       \resumeProjectHeading
%           {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
%           \resumeItemListStart
%             \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
%             \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
%             \resumeItem{Visualized GitHub data to show collaboration}
%             \resumeItem{Used Celery and Redis for asynchronous tasks}
%           \resumeItemListEnd
%       \resumeProjectHeading
%           {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
%           \resumeItemListStart
%             \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
%             \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
%             \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
%             \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
%           \resumeItemListEnd
%     \resumeSubHeadingListEnd

\vspace{2pt}

% \section{Academic Publications}
% \resumeSubHeadingListStart

%   \resumeSubItem{Michele Cattaneo; Eliã Batista; Fernando Pedone. \textbf{\textit{B+AVL trees: towards data structures for robust and efficient blockchain state synchronization}}. Proceedings of the 44th International Symposium on Reliable Distributed Systems, Porto, Portugal, 2025.}

%   \resumeSubItem{Eliã Batista; Paulo Coelho; Eduardo Alchieri; Fernando Dotti; Fernando Pedone. \textbf{\textit{FlexCast: Genuine Overlay-based Atomic Multicast}}. Proceedings of the 24th International Middleware Conference, Bologna, Italy, 2023.}

  
%   \resumeSubItem{Eliã Batista; Eduardo Alchieri; Fernando Dotti; Fernando Pedone. \textbf{\textit{Early Scheduling on Steroids: Boosting Parallel State Machine Replication}}. Journal of Parallel and Distributed Computing, Volume 163, May 2022.}
  
%   \resumeSubItem{Eliã Batista; Eduardo Alchieri; Fernando Dotti; Fernando Pedone. \textbf{\textit{Resource Utilization Analysis of Early Scheduling in Parallel State Machine Replication}}. Proceedings of the 9th Latin-American Symposium on Dependable Computing, Brazil, 2019.}
  
% \resumeSubHeadingListEnd

% \vspace{2pt}
% %
% %-----------PROGRAMMING SKILLS-----------

\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{
    \item \textbf{Languages}{: English (fluent), Italian (intermediate), Portuguese (native).} \\ [2mm]

    \item{\textbf{Programming Languages}{: Go, Java, Python, JavaScript, SQL, Bash Script.}} \\[2mm]
\item{\textbf{Backend \& Systems}{: RESTful API design, high-availability systems, distributed systems, debugging, performance optimization.}} \\[2mm]
\item{\textbf{Databases}{: SQLServer, MySQL, MongoDB, Firebase.}} \\[2mm]
\item{\textbf{Cloud \& DevOps}{: Linux, Docker, CI/CD pipelines, cloud deployment.}} \\[2mm]
\item{\textbf{Leadership}{: Technical leadership, mentoring, cross-team collaboration, project strategy and roadmap support.}} \\[2mm]
\item{\textbf{Soft Skills}{: Analytical problem-solving, capacity planning, experimental mindset, Agile methodologies.}}

    }
 \end{itemize}


%-------------------------------------------
\end{document}
