%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{changepage}


%----------FONT OPTIONS----------
% sans-serif
\usepackage[sfdefault]{FiraSans}
\usepackage[sfdefault]{roboto}
\usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% \pagestyle{fancy}
% \fancyhf{} % clear all header and footer fields
% \fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{.3in}
\addtolength{\topmargin}{-.5in}
% \addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 }%\vspace{2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\huge \scshape Eliã Rafael de Lima Batista} \\ \vspace{15pt}
    \small 77-992-5544 $|$ \href{mailto:o.elia.batista@gmail.com}{\underline{o.elia.batista@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/e-batista}{\underline{linkedin.com/in/e-batista}} $|$
    \href{https://elbatista.github.io}{\underline{elbatista.github.io}} \\
    \vspace{5pt}
    \small \emph{PhD Candidate in Informatics at University of Lugano (USI)} \\
    \vspace{5pt}
    \small 6963 Pregassona, TI, Switzerland \\
    % \vspace{5pt}
    % \small \emph{Working Permit: Swiss Permit B | Available for Relocation, Remote Work or Hybrid}
\end{center}

\vspace{2pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Lugano (USI)}{Lugano, Switzerland}
      {PhD in Informatics}{2021 -- Feb 2026}
    \resumeSubheading
      {PUC-RS}{Porto Alegre, Brazil}
      {MSc in Computer Science}{2018 -- 2020}
    \resumeSubheading
      {PUC-RS}{Porto Alegre, Brazil}
      {BSc in Computer Science}{2006 -- 2011}
  \resumeSubHeadingListEnd


  \vspace{2pt}

  \section{Professional Summary}

  \begin{adjustwidth}{0.15in}{0pt}
  \small
  Software engineer and researcher with over \textbf{15 years} of experience designing and implementing high-performance software and fault-tolerant systems. Currently a \textbf{\textsc{Ph.D.} candidate} and researcher at University of Lugano (\textsc{USI}), specializing in distributed systems. Proficient in \textbf{Java}, \textbf{Go}, \textbf{Python}, \textbf{C}, and \textbf{Linux environments}, with hands-on experience managing clusters and optimizing large-scale distributed applications. Former \textbf{Senior Software Developer} leading \textbf{full-stack} projects using \textbf{React} and \textbf{Node.js}. Passionate about building scalable, reliable software that bridges advanced research with real-world applications.


  \end{adjustwidth}

  \vspace{2pt}
%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Research and Development}{2021 -- Feb 2026}
      {University of Lugano (USI)}{Lugano, Switzerland}
      \resumeItemListStart
      \resumeItem{Conducted \textbf{research and development} in distributed dependable systems using \textbf{Java}, \textbf{Go}, \textbf{Python}, \textbf{C}, and \textbf{Bash} on \textbf{Linux} environments.}
      \resumeItem{Administered a \textbf{Linux cluster} supporting experimental distributed systems.}
      \resumeItem{Developed core SMR components and multicast algorithms focusing on \textbf{performance} and \textbf{fault tolerance}.}
      \resumeItem{Authored and reviewed papers for top distributed systems conferences.}
      \resumeItem{\textbf{Teaching assistant} for Operating Systems, Systems Programming, and Distributed Algorithms courses.}
            \resumeItemListEnd
      
    \resumeSubheading
      {Senior Software Developer}{2017 -- 2020}
      {Compasso UOL}{Brazil, RS}
      \resumeItemListStart
        % \resumeItem{Full-stack Web Developer | React, Node.js}
        % \resumeItem{Mobile App Developer | React Native, RESTful APIs}
        \resumeItem{Led the development of scalable full-stack web applications using \textbf{ReactJS} and \textbf{Node.js}, contributing to architecture decisions and continuous integration workflows.}
        \resumeItem{Built and maintained cross-platform mobile applications with \textbf{React Native}, integrating secure and performant \textbf{RESTful APIs} for enterprise clients.}
        \resumeItem{Collaborated with UI/UX designers to implement responsive, user-centric features, improving engagement and usability across platforms.}
        \resumeItem{Contributed to Agile processes (SCRUM), code reviews, and mentoring of junior developers in modern JavaScript and mobile best practices.}
    
     \resumeItemListEnd

     \clearpage

    \resumeSubheading
      {System Analyst}{2014 -- 2017}
      {Bem Promotora}{Brazil, RS}
      \resumeItemListStart
      \resumeItem{Developed and maintained ERP modules for a credit payroll loan financial company linked to Banrisul, a major bank in Southern Brazil}
      \resumeItem{Analyzed, documented, and communicated new system features to the development team to improve business process efficiency}
      \resumeItem{Implemented complex business rules and data processing using \textbf{SQL Server} stored procedures for accurate loan management and reporting}
      \resumeItem{Interacted closely with stakeholders to analyze requirements, define features, and ensure alignment with financial regulations and business needs}
        \resumeItemListEnd
     

    \resumeSubheading
      {Software Developer}{2010 -- 2013}
      {DBServer}{Brazil, RS}
      \resumeItemListStart
      \resumeItem{Developed and customized ERP modules using \textbf{Microsoft Visual Basic} tailored for a major fuel retail network (Ipiranga) in Brazil, improving operational efficiency and sales tracking}
      \resumeItem{Integrated and managed backend logic with \textbf{SQL Server} for efficient data storage and retrieval}
     \resumeItemListEnd

     \resumeSubheading
     {Software Developer}{2008 -- 2010}
     {Vensis}{Brazil, RS}
     \resumeItemListStart
     \resumeItem{Built and maintained general-purpose ERP modules with \textbf{Microsoft Visual Basic}, adaptable for various enterprise environments}
     \resumeItem{Optimized \textbf{SQL Server} queries and stored procedures to boost system performance and data consistency}
     \resumeItemListEnd


  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
% \section{Projects}
%     \resumeSubHeadingListStart
%       \resumeProjectHeading
%           {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
%           \resumeItemListStart
%             \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
%             \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
%             \resumeItem{Visualized GitHub data to show collaboration}
%             \resumeItem{Used Celery and Redis for asynchronous tasks}
%           \resumeItemListEnd
%       \resumeProjectHeading
%           {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
%           \resumeItemListStart
%             \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
%             \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
%             \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
%             \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
%           \resumeItemListEnd
%     \resumeSubHeadingListEnd

\vspace{2pt}

\section{Academic Publications}
\resumeSubHeadingListStart

  \resumeSubItem{Michele Cattaneo; Eliã Batista; Fernando Pedone. \textbf{\textit{B+AVL trees: towards data structures for robust and efficient blockchain state synchronization}}. Proceedings of the 44th International Symposium on Reliable Distributed Systems, Porto, Portugal, 2025.}
  \resumeSubItem{Eliã Batista; Paulo Coelho; Eduardo Alchieri; Fernando Dotti; Fernando Pedone. \textbf{\textit{FlexCast: Genuine Overlay-based Atomic Multicast}}. Proceedings of the 24th International Middleware Conference, Bologna, Italy, 2023.}

  
  \resumeSubItem{Eliã Batista; Eduardo Alchieri; Fernando Dotti; Fernando Pedone. \textbf{\textit{Early Scheduling on Steroids: Boosting Parallel State Machine Replication}}. Journal of Parallel and Distributed Computing, Volume 163, May 2022.}
  
  \resumeSubItem{Eliã Batista; Eduardo Alchieri; Fernando Dotti; Fernando Pedone. \textbf{\textit{Resource Utilization Analysis of Early Scheduling in Parallel State Machine Replication}}. Proceedings of the 9th Latin-American Symposium on Dependable Computing, Brazil, 2019.}
  
\resumeSubHeadingListEnd

\vspace{2pt}
%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Languages}{: English (fluent), Italian (intermediate), Portuguese (native)} \\ \vspace{2mm}
     \textbf{Programming Languages}{: Java, Go, Visual Basic, JavaScript} \\ \vspace{2mm}
     \textbf{Frameworks \& Methodologies}{: React, Node.js, Next.js} \\ \vspace{2mm}
     \textbf{Developer Tools \& Platforms}{: Git, Maven, Gradle, REST APIs} \\ \vspace{2mm}
     \textbf{Databases \& Storage}{: SQL Server, PostgreSQL, MongoDB, Firebase DB} \\ \vspace{2mm}
    %  \textbf{Cloud Services}{: Firebase Hosting, Firebase Authentication, Firebase Functions, Basic knowledge of AWS cloud services} \\ \vspace{2mm}
     \textbf{Distributed Systems}{: State Machine Replication, Consensus, Paxos, Atomic Multicast} \\ \vspace{2mm}
    %  \textbf{Personal Hobby Project}{: \href{https://wondersofswitzerland.com/}{\underline{wondersofswitzerland.com}} — a hobby project written in Next.js showcasing family-friendly destinations for tourists across Switzerland}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
