%-------------------------
% Resume in Latex - Tailored for KAIROS project
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{changepage}

%----------FONT OPTIONS----------
\usepackage[sfdefault]{sourcesanspro}

% Adjust margins
\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{.3in}
\addtolength{\topmargin}{-.5in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\huge \scshape Eliã Rafael de Lima Batista} \\ \vspace{10pt}
    \small 77-992-5544 $|$ \href{mailto:o.elia.batista@gmail.com}{o.elia.batista@gmail.com} $|$ 
    \href{https://www.linkedin.com/in/e-batista}{linkedin.com/in/e-batista} $|$
    \href{https://elbatista.github.io}{elbatista.github.io} \\
    \vspace{3pt}
    \small \emph{PhD Candidate in Informatics, Distributed Systems Researcher} \\
    \small 6963 Pregassona, TI, Switzerland
\end{center}

\vspace{2pt}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Università della Svizzera italiana (USI)}{Lugano, Switzerland}
      {PhD in Informatics, Distributed Systems}{2021 -- Feb 2026}
    \resumeSubheading
      {PUC-RS}{Brazil}
      {MSc in Computer Science}{2018 -- 2020}
    \resumeSubheading
      {PUC-RS}{Brazil}
      {BSc in Computer Science}{2006 -- 2011}
\resumeSubHeadingListEnd

\vspace{2pt}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\begin{adjustwidth}{0.15in}{0pt}
\small
Distributed systems researcher and software engineer with \textbf{10+ years} of experience designing scalable, fault-tolerant architectures and high-performance software. Focused on \textbf{incremental computation, real-time performance, and distributed state management}. Experienced in implementing \textbf{distributed middleware, SMR, and consensus protocols}, bridging cutting-edge research with practical enterprise deployments. Skilled in \textbf{Java, Go, Python, C}, and cluster management in Linux environments. Passionate about integrating \textbf{knowledge graphs, AI agents, and LLMs} for real-time, adaptive decision-making systems.
\end{adjustwidth}

\vspace{2pt}

%-----------EXPERIENCE-----------
\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Research and Development}{2021 -- Feb 2026}
{University of Lugano (USI)}{Lugano, Switzerland}
\resumeItemListStart
\resumeItem{Designed and implemented \textbf{distributed fault-tolerant systems} supporting high-throughput, low-latency operations on dynamic datasets.}
\resumeItem{Developed core \textbf{State Machine Replication (SMR)} and \textbf{Atomic Multicast} components with incremental state management.}
\resumeItem{Optimized distributed middleware for \textbf{real-time performance and iterative processing}.}
\resumeItem{Administered a \textbf{Linux cluster} supporting experimental deployments of scalable distributed algorithms.}
\resumeItem{Authored papers in top conferences and journals on distributed state management, fault tolerance, and parallel SMR.}
\resumeItem{Teaching assistant for \textbf{Operating Systems, Systems Programming, and Distributed Algorithms}.}
\resumeItemListEnd

\resumeSubheading
{Senior Software Developer}{2017 -- 2020}
{Compasso UOL}{Brazil, RS}
\resumeItemListStart
\resumeItem{Led development of \textbf{scalable full-stack applications} and backend services for enterprise clients.}
\resumeItem{Implemented RESTful APIs for dynamic data access and optimized data pipelines for performance and reliability.}
\resumeItem{Mentored junior developers on software architecture and distributed application design.}
\resumeItemListEnd

\resumeSubheading
{System Analyst}{2014 -- 2017}
{Bem Promotora}{Brazil, RS}
\resumeItemListStart
\resumeItem{Analyzed and optimized ERP modules, implementing \textbf{efficient data processing pipelines} with SQL Server.}
\resumeItem{Documented and communicated requirements, ensuring alignment with business rules and regulatory constraints.}
\resumeItemListEnd


\resumeSubheading
{Software Developer}{2010 -- 2013}
{DBServer}{Brazil, RS}
\resumeItemListStart
\resumeItem{Developed and customized ERP modules using \textbf{Microsoft technologies} tailored for a major fuel retail network in Brazil, improving operational efficiency and sales tracking}
\resumeItem{Integrated and managed backend logic with \textbf{SQL Server} for efficient data storage and retrieval}
\resumeItemListEnd

\resumeSubheading
{Software Developer}{2008 -- 2010}
{Vensis}{Brazil, RS}
\resumeItemListStart
\resumeItem{Built and maintained general-purpose ERP modules with \textbf{Microsoft technologies}, adaptable for various enterprise environments}
\resumeItem{Optimized \textbf{SQL Server} queries and stored procedures to boost system performance and data consistency}
\resumeItemListEnd



\resumeSubHeadingListEnd

\vspace{2pt}

%-----------ACADEMIC PUBLICATIONS-----------
\section{Academic Publications}
\resumeSubHeadingListStart
\resumeSubItem{Michele Cattaneo; Eliã Batista; Fernando Pedone. \textbf{\textit{B+AVL trees: towards data structures for robust and efficient blockchain state synchronization}}. Proceedings of the 44th International Symposium on Reliable Distributed Systems, 2025.}
\resumeSubItem{Eliã Batista; Paulo Coelho; Eduardo Alchieri; Fernando Dotti; Fernando Pedone. \textbf{\textit{FlexCast: Genuine Overlay-based Atomic Multicast}}. Proceedings of the 24th International Middleware Conference, 2023.}
\resumeSubItem{Eliã Batista; Eduardo Alchieri; Fernando Dotti; Fernando Pedone. \textbf{\textit{Early Scheduling on Steroids: Boosting Parallel State Machine Replication}}. Journal of Parallel and Distributed Computing, 2022.}
\resumeSubItem{Eliã Batista; Eduardo Alchieri; Fernando Dotti; Fernando Pedone. \textbf{\textit{Resource Utilization Analysis of Early Scheduling in Parallel State Machine Replication}}. Latin-American Symposium on Dependable Computing, 2019.}
\resumeSubHeadingListEnd

\vspace{2pt}

%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small
\item{
  \textbf{Programming:} Java, Go, Python, C, Visual Basic, JavaScript\\
  \textbf{Frameworks \& Methodologies:} React, Node.js, Next.js, Agile/SCRUM\\
  \textbf{Developer Tools:} Git, Maven, Gradle, REST APIs, Linux Cluster Administration\\
  \textbf{Databases \& Storage:} SQL Server, PostgreSQL, MongoDB, Firebase DB, Graph Databases (Neo4j)\\
  \textbf{Distributed Systems:} State Machine Replication, Consensus, Paxos, Atomic Multicast, Incremental Computation, Fault-Tolerant Middleware\\
  \textbf{AI \& Knowledge Systems:} Knowledge Graphs, LLM Integration, Retrieval-Augmented Generation (RAG), Real-Time Reasoning}\\
  \textbf{Languages:} English (fluent), Italian (intermediate), Portuguese (native)
\end{itemize}

\end{document}
