% Tailored CV for Swissquote - Senior Backend Software Engineer

%-------------------------
% Resume in Latex (Updated for Swissquote)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{changepage}
\usepackage{ragged2e}

% Fonts
\usepackage[sfdefault]{sourcesanspro}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{.3in}
\addtolength{\topmargin}{-.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Commands
\newcommand{\resumeItem}[1]{
  \item\small \justifying{#1 }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\huge \scshape Eliã Rafael de Lima Batista} \\ \vspace{12pt}
    \small 77-992-5544 $|$ \href{mailto:o.elia.batista@gmail.com}{\underline{o.elia.batista@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/e-batista}{\underline{linkedin.com/in/e-batista}} $|$
    \href{https://elbatista.github.io}{\underline{elbatista.github.io}} \\ \vspace{5pt}
    \small 6963 Pregassona, Ticino, Switzerland \\ 
    \textit{Valid Swiss Work Permit | Available to relocate or commute}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textsc{Ph.D.} in Informatics}{2021 -- Feb 2026 (expected)}
      {Università della Svizzera Italiana (USI)}{Lugano, Switzerland}
    \resumeSubheading
      {\textsc{M.Sc.} in Computer Science}{2018 -- 2020}
      {Pontifical Catholic University of Rio Grande do Sul (PUC-RS)}{Porto Alegre, Brazil}
    \resumeSubheading
      {\textsc{B.Sc.} in Computer Science}{2006 -- 2011}
      {Pontifical Catholic University of Rio Grande do Sul (PUC-RS)}{Porto Alegre, Brazil}
  \resumeSubHeadingListEnd

%-----------SUMMARY-----------
\section{Professional Summary}
\begin{adjustwidth}{0.15in}{0pt}
\small
\justifying
Backend-focused Software Engineer with 10+ years of experience in \textbf{Java}, distributed systems, backend services, and event-driven architectures. Strong background in \textbf{Spring/Spring Boot}, \textbf{JPA/Hibernate}, REST APIs, and messaging systems. Experience building fault-tolerant systems, developing performance-oriented backend components, and deploying production services. Passionate about financial systems, trading platforms, and scalable backend architectures.
\end{adjustwidth}

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Research and Development Engineer}{2021 -- Present}
      {Università della Svizzera Italiana (USI)}{Lugano, Switzerland}
      \resumeItemListStart
        \resumeItem{Designed and implemented core components for \textbf{fault-tolerant distributed systems} using \textbf{Java, Go, and Python}.}
        \resumeItem{Developed high-performance replicated system modules with focus on \textbf{state management, recovery, and message ordering}.}
        \resumeItem{Worked with event-driven designs and communication overlays relevant to \textbf{atomic multicast} and real-time message processing.}
        \resumeItem{Administered and optimized a \textbf{Linux cluster}, including deployment, testing, and monitoring workflows.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Software Developer}{2017 -- 2020}
      {Compasso UOL}{Brazil}
      \resumeItemListStart
        \resumeItem{Led development of production-grade backend and full-stack applications using \textbf{Java, Node.js, React}, and RESTful APIs.}
        \resumeItem{Integrated complex business logic and contributed to scalable, modular backend architectures.}
        \resumeItem{Participated in \textbf{code reviews, CI/CD}, and team mentoring.}
      \resumeItemListEnd

    \resumeSubheading
      {System Analyst}{2014 -- 2017}
      {Bem Promotora}{Brazil}
      \resumeItemListStart
        \resumeItem{Developed \textbf{financial and loan-processing} ERP modules using SQL Server and enterprise backend patterns.}
        \resumeItem{Implemented data workflows and business rules ensuring accurate settlement and reporting processes.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{2010 -- 2013}
      {DBServer}{Brazil}
      \resumeItemListStart
        \resumeItem{Developed backend modules and ERP features for major retail clients using Microsoft technologies.}
        \resumeItem{Designed efficient database procedures and optimized SQL queries for high-volume operations.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{2008 -- 2010}
      {Vensis}{Brazil}
      \resumeItemListStart
        \resumeItem{Built general-purpose ERP modules and backend business logic.}
        \resumeItem{Optimized SQL Server operations, improving system performance and stability.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small
    \item{\textbf{Java Ecosystem}{: Java 8--21, Spring Boot, Hibernate/JPA, Maven, Gradle.} \\ \vspace{2mm}
    \textbf{Event-Driven \& Messaging}{: Kafka, RabbitMQ (experience with distributed communication patterns).} \\ \vspace{2mm}
    \textbf{DevOps \& Tools}{: Docker, Jenkins, GitHub, CI/CD pipelines.} \\ \vspace{2mm}
    \textbf{Databases}{: PostgreSQL, MySQL, SQL Server, MongoDB, FirebaseDB.} \\ \vspace{2mm}
    \textbf{Cloud}{: AWS (basic), Linux server administration.} \\ \vspace{2mm}
    \textbf{Languages}{: English (fluent), Italian (intermediate), Portuguese (native).}}
 \end{itemize}

\end{document}
