%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{changepage}
\usepackage{ragged2e} % add this in the preamble


%----------FONT OPTIONS----------
% sans-serif
\usepackage[sfdefault]{FiraSans}
\usepackage[sfdefault]{roboto}
\usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}


\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{.3in}
\addtolength{\topmargin}{-.5in}
% \addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small \justifying{
    {#1 }%\vspace{2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\begin{document}


\begin{center}
    \textbf{\huge \scshape Eliã Rafael de Lima Batista} \\ \vspace{15pt}
    \small 77-992-5544 $|$ \href{mailto:o.elia.batista@gmail.com}{\underline{o.elia.batista@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/e-batista}{\underline{linkedin.com/in/e-batista}} $|$
    \href{https://elbatista.github.io}{\underline{elbatista.github.io}} \\
    \vspace{5pt}
    \small 6963 Pregassona, TI, Switzerland\\
    \vspace{5pt}
    \small \emph{Valid B Working Permit for Switzerland }
\end{center}

\vspace{2pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textsc{Ph.D.} in Informatics}{2021 -- Feb 2026}
      {Università della Svizzera Italiana (USI)}{Lugano, Switzerland}
    \resumeSubheading
      {\textsc{M.Sc.} in Computer Science}{2018 -- 2020}
      {Pontifical Catholic University of Rio Grande do Sul (PUC-RS)}{Porto Alegre, Brazil}
    \resumeSubheading
      {\textsc{B.Sc.} in Computer Science}{2006 -- 2011}
      {Pontifical Catholic University of Rio Grande do Sul (PUC-RS)}{Porto Alegre, Brazil}
  \resumeSubHeadingListEnd

\vspace{2pt}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\begin{adjustwidth}{0.15in}{0pt}
\small
\justifying
Software engineer and researcher with \textbf{10+ years of experience} designing scalable, high-performance software and distributed systems. Skilled in \textbf{ReactJS, Next.js, TypeScript, Node.js, and cloud-based frontend development}, with strong expertise in \textbf{user-facing features, automated testing (TDD/BDD), and Agile workflows}. Experienced in \textbf{Linux environments}, system optimization, and leading development teams. Passionate about building robust, secure, and maintainable software that connects cutting-edge technology to real-world impact.
\end{adjustwidth}

\vspace{2pt}

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Research and Development}{2021 -- Present}
      {Università della Svizzera Italiana (USI)}{Lugano, Switzerland}
      \resumeItemListStart
        \resumeItem{Designed and implemented distributed systems and cloud-based components in \textbf{Java, Go, and Python}, focusing on \textbf{performance, scalability, and fault tolerance}.}
        \resumeItem{Implemented automated testing and CI pipelines to ensure high-quality software releases.}
        \resumeItem{Teaching assistant for Operating Systems, Systems Programming, and Distributed Algorithms; mentored students in best practices for software design, testing, and agile development.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Software Developer}{2017 -- 2020}
      {Compasso UOL}{Brazil, RS}
      \resumeItemListStart
        \resumeItem{Led frontend and full-stack development using \textbf{ReactJS, Next.js, React Native, Node.js, and TypeScript}, delivering scalable user-facing features.}
        \resumeItem{Integrated secure and performant \textbf{RESTful APIs} for enterprise applications.}
        \resumeItem{Implemented \textbf{automated testing} (unit, integration) to reduce bugs and maintain high-quality releases.}
        \resumeItem{Collaborated with designers and product owners in an \textbf{Agile SCRUM environment} to deliver user-centric solutions efficiently.}
        \resumeItem{Mentored junior developers in ReactJS, TypeScript, and cloud frontend development best practices.}
      \resumeItemListEnd

    \resumeSubheading
      {System Analyst}{2014 -- 2017}
      {Bem Promotora}{Brazil, RS}
      \resumeItemListStart
        \resumeItem{Developed ERP modules and backend services using \textbf{SQL Server}, optimizing data workflows and system performance.}
        \resumeItem{Collaborated with stakeholders to design and implement user-facing features for internal enterprise tools.}
        \resumeItemListEnd

    \resumeSubheading
      {Software Developer}{2010 -- 2013}
      {DBServer}{Brazil, RS}
      \resumeItemListStart
        \resumeItem{Developed ERP modules with \textbf{Microsoft Visual Basic} and \textbf{SQL Server}, improving operational efficiency.}
      \resumeItemListEnd

     \resumeSubheading
      {Software Developer}{2008 -- 2010}
      {Vensis}{Brazil, RS}
      \resumeItemListStart
        \resumeItem{Built and maintained ERP modules, optimizing database queries and performance with \textbf{SQL Server}.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\vspace{2pt}

%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{
\item{
\textbf{Programming Languages:} JavaScript, TypeScript, Java, Go, Python, HTML/CSS, SQL, C/C++, PHP, Visual Basic \\ \vspace{1mm}
\textbf{Frontend/Cloud Frameworks:} ReactJS, Next.js, React Native, Node.js, REST APIs, Firebase, AWS (basic) \\ \vspace{1mm}
\textbf{Testing:} TDD, BDD, unit/integration testing, automated pipelines \\ \vspace{1mm}
\textbf{Methodologies:} Agile, SCRUM, CI/CD workflows \\ \vspace{1mm}
\textbf{Databases:} SQL Server, PostgreSQL, MongoDB, Firebase Realtime Database \\ \vspace{1mm}
\textbf{Distributed Systems:} State Machine Replication, Multicast Protocols, State Management, Scalable architectures \\ \vspace{1mm}
\textbf{Languages:} English (fluent), Italian (intermediate), Portuguese (native)
}}
\end{itemize}



\end{document}
