% Tailored CV for Blockchain Systems Architect Role

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{changepage}

\usepackage[default]{sourcesanspro}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.2in}
\addtolength{\evensidemargin}{-0.2in}
\addtolength{\textwidth}{.3in}
\addtolength{\topmargin}{-.5in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 }}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\huge \scshape Eliã Rafael de Lima Batista} \\ \vspace{12pt}
    \small 77-992-5544 $|$ \href{mailto:o.elia.batista@gmail.com}{\underline{o.elia.batista@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/e-batista}{\underline{linkedin.com/in/e-batista}} $|$ 
    \href{https://elbatista.github.io}{\underline{elbatista.github.io}} \\ \vspace{5pt}
    \small 6963 Pregassona, Ticino, Switzerland \\ 
    \textit{Valid Swiss Work Permit | Available to relocate or commute}
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading{University of Lugano (USI)}{Lugano, Switzerland}{PhD in Informatics}{2021 -- Feb 2026}
    \resumeSubheading{PUC-RS}{Porto Alegre, Brazil}{MSc in Computer Science}{2018 -- 2020}
    \resumeSubheading{PUC-RS}{Porto Alegre, Brazil}{BSc in Computer Science}{2006 -- 2011}
  \resumeSubHeadingListEnd

\section{Professional Summary}
\begin{adjustwidth}{0.15in}{0pt}
\small
Systems architect and software engineer with over 15 years of experience in designing, developing, and optimizing distributed and fault-tolerant systems. Expertise in \textbf{Java, Go, Python, C}, and distributed system frameworks. Skilled in blockchain technologies, consensus algorithms, and secure high-performance computing. Proven ability to lead architectural design, technical decision-making, and system implementation for complex financial and experimental systems.
\end{adjustwidth}

\section{Professional Experience}
\resumeSubHeadingListStart

\resumeSubheading{Researcher and Teaching Assistant}{2021 -- Present}{University of Lugano (USI)}{Lugano, Switzerland}
\resumeItemListStart
\resumeItem{Lead the design and development of fault-tolerant distributed systems, including SMR and atomic multicast frameworks, using \textbf{Java, Go, Python, and C}.}
\resumeItem{Implemented blockchain-related research prototypes, focusing on consensus, reliability, and performance.}
\resumeItem{Administered and optimized Linux clusters for high-performance and secure experiments.}
\resumeItem{Provided architectural guidance and code review for experimental distributed system components.}
\resumeItem{Teaching assistant for Operating Systems, Distributed Algorithms, and Systems Programming courses.}
\resumeItemListEnd

\resumeSubheading{Senior Software Developer}{2017 -- 2020}{Compasso UOL}{Brazil, RS}
\resumeItemListStart
\resumeItem{Led full-stack and backend architecture for enterprise applications, ensuring scalability, security, and reliability.}
\resumeItem{Contributed to technical decision-making, system design, and CI/CD pipelines.}
\resumeItem{Mentored developers and collaborated on architecture discussions to align on high-quality solutions.}
\resumeItemListEnd

\resumeSubheading{System Analyst}{2014 -- 2017}{Bem Promotora}{Brazil, RS}
\resumeItemListStart
\resumeItem{Developed financial ERP modules and backend systems with a focus on stability, security, and compliance.}
\resumeItem{Analyzed complex system requirements and translated them into technical designs and processes.}
\resumeItemListEnd

\resumeSubheading{Software Developer}{2010 -- 2013}{DBServer}{Brazil, RS}
\resumeItemListStart
\resumeItem{Built ERP backend modules and optimized SQL Server workflows to ensure performance and consistency.}
\resumeItemListEnd

\resumeSubheading{Software Developer}{2008 -- 2010}{Vensis}{Brazil, RS}
\resumeItemListStart
\resumeItem{Developed and maintained ERP and backend solutions using Microsoft technologies, focusing on robust design and maintainability.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Academic Publications}
\resumeSubHeadingListStart
\resumeSubItem{Michele Cattaneo; Eliã Batista; Fernando Pedone. \textbf{B+AVL trees: towards data structures for robust and efficient blockchain state synchronization}. Proceedings of the 44th International Symposium on Reliable Distributed Systems, 2025.}
\resumeSubItem{Eliã Batista; Paulo Coelho; Eduardo Alchieri; Fernando Dotti; Fernando Pedone. \textbf{FlexCast: Genuine Overlay-based Atomic Multicast}. Proceedings of the 24th International Middleware Conference, 2023.}
\resumeSubItem{Eliã Batista; Eduardo Alchieri; Fernando Dotti; Fernando Pedone. \textbf{Early Scheduling on Steroids: Boosting Parallel State Machine Replication}. Journal of Parallel and Distributed Computing, 2022.}
\resumeSubItem{Eliã Batista; Eduardo Alchieri; Fernando Dotti; Fernando Pedone. \textbf{Resource Utilization Analysis of Early Scheduling in Parallel State Machine Replication}. Proceedings of the 9th Latin-American Symposium on Dependable Computing, 2019.}
\resumeSubHeadingListEnd

\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Languages}: English (fluent), Italian (intermediate), Portuguese (native) \\ \vspace{2mm}
\textbf{Programming}: Java, Go, Python, C, Visual Basic \\ \vspace{2mm}
\textbf{Distributed Systems}: Consensus, Paxos, SMR, Atomic Multicast, Blockchain architecture \\ \vspace{2mm}
\textbf{DevOps/Tools}: Git, Maven, Gradle, REST APIs, Linux administration \\ \vspace{2mm}
\textbf{Blockchain \& Security}: Cryptography, secure distributed protocols, fault tolerance, state management, authenticated data structures \\ \vspace{2mm}
\textbf{Frameworks}: ReactJS, Node.js, Next.js
}}
\end{itemize}

\end{document}