\documentclass[11pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=1in]{geometry}

\begin{document}

\begin{letter}{Hiring Team\\[1mm] [Company Name]\\[1mm] [Company Address]}

\opening{Dear Hiring Team,}

I am writing to express my interest in the Blockchain Systems Architect position at [Company Name]. With over 15 years of experience in software engineering and research, I have developed a strong foundation in designing, implementing, and optimizing high-performance distributed systems. My PhD research at the University of Lugano (\textsc{USI}) focuses on State Machine Replication, consensus algorithms, and fault-tolerant architectures—skills that I am eager to apply in building secure and scalable blockchain infrastructure.

Throughout my career, I have demonstrated a consistent ability to bridge research and practical application. At USI, I led the development of core distributed system components using \textbf{Java, Go, Python, and C} and administered Linux clusters for high-performance experiments. Previously, as a Senior Software Developer at Compasso UOL, I led full-stack and backend projects, shaping system architecture decisions, ensuring reliability, and mentoring developers. These experiences have honed my technical decision-making, system-level thinking, and ability to design for both performance and resilience—key qualities for this role.

The opportunity to contribute to cutting-edge blockchain solutions in the financial space excites me deeply. I am particularly motivated by the challenge of designing consensus frameworks and secure systems that combine innovation with stability. My academic publications, including research on blockchain state synchronization and atomic multicast systems, reflect my passion for distributed systems and blockchain technologies, and I am eager to bring this expertise to your team.

I am confident that my combination of hands-on engineering experience, research background, and leadership in system architecture make me a strong fit for this position. I hold a valid Swiss work permit and am available to relocate or commute as needed.

I invite you to review my professional work and projects through the following links:  
\begin{itemize}
    \item GitHub: \href{https://github.com/elbatista}{https://github.com/elbatista}  
    \item LinkedIn: \href{https://www.linkedin.com/in/e-batista}{https://www.linkedin.com/in/e-batista}  
    \item Portfolio: \href{https://elbatista.github.io}{https://elbatista.github.io}  
\end{itemize}

Thank you for considering my application. I am enthusiastic about the possibility of contributing to your team and would welcome the opportunity to discuss how my experience and skills align with your vision.

\closing{Sincerely,\\[2mm] Eliã Rafael de Lima Batista}

\end{letter}
\end{document}
